---
title: "Visualize Housing Data with WalkScore"
author: "Wenting Feng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

Here's some examples on what we can do with the aggregated Housing Return on Equity(ROE) data with WalkScore. 

## Data visualization with HousingROE

In overview of ROE data divided by walk score and beds, we can make a plot as following to sow the distribution(some outliers of the beds are removed). 

```{r}
library(ggplot2)
library(HousingROE)
ManhattanPlot <- ggplot(datot[datot$beds != "1.5 beds" & datot$beds != "10 beds", ], aes(x=beds, y=roe)) 
ManhattanPlot +
    geom_boxplot(aes(fill=factor(walk_score)), alpha=0.5)
```

## Spatial Visualization through ggmap

Given the `datot` dataset we just collected and cleaned for Manhattan ROE, we are able to conduct the visualization through geographical mapping as well. 

```{r}
library(ggmap)
ManhattanMap <- qmap(location = "Manhattan", zoom = 12, color = "bw")
ManhattanMap + 
    geom_point(aes(x = longitude, y = latitude, color = roe, size = roe), alpha = 0.5, data = datot)
```

> "D. Kahle and H. Wickham. ggmap: Spatial Visualization with ggplot2. The R Journal,5(1), 144-161."([via](http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf))
